The importance of serve in table tennis

### 2021-02-07 inst/table_tennis_serve.Rmd
consistentify table tennis

```{r}
H
```

@@

```{r}
p1 <- maxp(H)
p1
```

And we can find the support at this point:

```{r}
maxlike_free <- loglik(indep(p1),H)
maxlike_free
```

@@

To do this we follow the protocol in the `icons` vignette.  First find
the MLE conditional on the serve having zero strength:

```{r}
small <- 1e-3
maxlike_constrained <-
    maxp(
        H,
        startp=c(small/2, 1/3-small/2, 1/3-small/2),
        fcm=c(-1,0,0),  fcv=-small,give=TRUE
)

maxlike_constrained
```

The difference in support is:

```{r}    	    
delta_support <- maxlike_free - maxlike_constrained$value
delta_support
```

and the likelihood ratio is:
```{r}
LR <- exp(delta_support)
LR
```

The difference in support, `delta_support`, is about 2.62 which
exceeds Edwards's two-units-of-support criterion.  We can reject the
null.  Alternatively, Wilks's theorem gives us that
$\Lambda=2\log(LR)$ is distributed as chi-squared with one degree of
freedom:

```{r}
Lambda <- 2*delta_support
pval <- pchisq(Lambda,df=1,lower.tail=FALSE)
pval 
```

@@

```{r}
maxp(H)
```

@@

```{r}
profile_likelihood <- function(S,give=FALSE){
    small <- 1e-2  # cannot make this too small, optimization routine needs wiggle room
    out <- maxp(
       H, startp=c(S+small/2 , small,small),
       give=TRUE,
       fcm=rbind(c(1,0,0),c(-1,0,0)),fcv=c(S,-S-small)  # S <= p[1] <= S+small
       )
    if(give){
       return(out)
      } else {
       return(out$value)
      }
}
```

We can then evaluate the profile likelihood for a range of possible
values of $S$:

```{r}
S_vals <- seq(from=0.02,to=0.85,len=30)  # possible values for S
prof_like <- sapply(S_vals,profile_likelihood)  
plot(S_vals, prof_like-max(prof_like),xlab="serve strength",ylab="profile likelihood")
abline(h= -2)
```

@@

>>>>

```{r}
table_tennis <- H
table_tennis
```

@@

```{r}
table_tennis_maxp <- maxp(table_tennis)
table_tennis_maxp
```

@@

```{r testservezero}
specificp.test(table_tennis,"S",0.01)
```

@@

```{r}
maxp(table_tennis)
```

@@

```{r}
S_vals <- seq(from=0.02,to=0.85,len=30)  # possible values for S
plot(S_vals,profsupp(table_tennis,"S",S_vals))
abline(h=c(0,-2))
```

@@

### Package dataset

Following lines create `table_tennis.rda`, residing in the `data/`
directory of the package.

```{r,label=savetabletennisdataset}
save(table_tennis,file="table_tennis.rda")
```
